On $K_2$-analogue of Serre problem for $\SL_4$

### 2018-08-07 paper.tex
Minor

The aim of this subsection is to demonstrate an analogue of~\cite[Lemma~3.3]{Tu83}. 
It is clear that the natural embedding of generators $\mathcal{X}_n \subseteq \mathcal{X}_{n+1}$ induces
 a map $\theta_n\colon G_n \to G_{n+1}$ for $n\geq 2$.
\begin{lemma}\label{lem:tul3.3}
 Let $\Phi$ be a simply-laced root systems of rank $\geq 3$.

 Moreover, the map $\theta_1\colon G_1/H \to G_2$ induced by  is isomorphic to $G_1$.
\end{lemma}
Unfortunately, the lemma cannot be proved by a slight modification of the original short argument of Tulenbayev.
 %for even in the linear case it works only for $\mathrm{rk}(\Phi)\geq 4$, and, in particular, is unsuitable in the case $\Phi=\mathsf{D}_\ell$.
Instead, we have to employ a varition of a much longer argument of U.~Rehmann and C.~Soul{\'e}, cf~\cite{Re75,RS76}.

@@

\begin{dfn} A pair of mutually inverse maps $(\sigma_i^+, \sigma_i^-)$ between the groups $N^i$ and $N_i$ will be called a {\it $\sigma$-pair corresponding to the vertex $i\in D(\Phi)$},
 if these maps fit into the following diagram.
\begin{equation} \label{eq:sigma-diagram}
\xymatrix{ N_i\ar@{-->}[r]^{\sigma_i^+}\ar[d] & N^i \ar[d] \ar@{-->}[r]^{\sigma_i^-} & N_i \ar[d] \\ 
          \St(\Phi, R) \ar@<-0.0ex>[r]_{\beta_i^+} & \St(\Phi, R) \ar@<-0.0ex>[r]_{\beta_i^-} & \St(\Phi, R)} 
\end{equation}
In the above diagram the vertical arrows are canonical embeddings of $N_k$ and $N^k$ into $\St(\Phi, A[t])$ postcomposed with 
 the map of Steinberg groups induced by the embedding $A[t] \hookrightarrow R$.
%As before, we denote by $R$ the ring $A[t, t^{-1}]$ of Laurent polynomials over $A$.
         % \GL(n, R) \ar@<-0.0ex>[r]_{(-)^{\delta_k}} & \GL(n, R) \ar@<-0.0ex>[r]_{{}^{\delta_k}(-)} & \GL(n, R)
\end{dfn}

>>>>

It is clear that the natural embedding of generators $\mathcal{X}_n \subseteq \mathcal{X}_{n+1}$ induces
 a map $\theta_n\colon G_n \to G_{n+1}$.
The aim of this subsection is to demonstrate an analogue of~\cite[Lemma~3.3]{Tu83}. 
\begin{lemma}\label{lem:tul3.3}
 Let $\Phi$ be a simply-laced root systems of rank $\geq 3$. 
 Then $ $
 Moreover, the map $\theta_1\colon G_1/H \to G_2$ induced by  is isomorphic to $G_1$.
\end{lemma}
Unfortunately, the lemma cannot be proved by a slight modification of the original short argument of Tulenbayev.
 %for even in the linear case it works only for $\mathrm{rk}(\Phi)\geq 4$, and, in particular, is unsuitable in the case $\Phi=\mathsf{D}_\ell$.
Instead, we have to employ a varition of a much longer argument of U.~Rehmann and C.~Soul{\'e}, cf~\cite{Re75,RS76}.

@@

\begin{dfn} A pair of mutually inverse maps $(\sigma_i^+, \sigma_i^-)$ between the groups $N^i$ and $N_i$ will be called a {\it $\sigma$-pair corresponding to the vertex $i\in D(\Phi)$},
 if these maps fit into the following diagram.
\begin{equation} \label{eq:sigma-diagram}
\xymatrix{ N_i\ar@{-->}[r]^{\sigma_i^+}\ar[d] & N^i \ar[d] \ar@{-->}[r]^{\sigma_i^-} & N_i \ar[d] \\ 
          \St(\Phi, R) \ar@<-0.0ex>[r]_{\beta_i^+} & \St(\Phi, R) \ar@<-0.0ex>[r]_{\beta_i^-} & \St(\Phi, R)} 
\end{equation}
In the above diagram the vertical arrows are canonical embeddings of $N_k$ and $N^k$ into $\St(\Phi, A[t])$ postcomposed with 
 the map of Steinberg groups induced by the embedding $A[t] \hookrightarrow R = A[t, t^{-1}]$.
%As before, we denote by $R$ the ring $A[t, t^{-1}]$ of Laurent polynomials over $A$.
         % \GL(n, R) \ar@<-0.0ex>[r]_{(-)^{\delta_k}} & \GL(n, R) \ar@<-0.0ex>[r]_{{}^{\delta_k}(-)} & \GL(n, R)
\end{dfn}
